---
title: "RandomForest Landcover classification - superClass"
author: "Luisa Pflumm"
date: "25 3 2022"
output:
  html_document:
    code_folding: hide
    collapsed: no
    toc: yes
    toc_depth: 4
    toc_float: yes
  <span style="color: red;">text</span>
---

<!-- Sources:  -->
<!-- https://valentinitnelav.github.io/satellite-image-classification-r/#fit_models -->
<!-- https://rspatial.org/raster/rs/5-supclassification.html#reference-data -->
<!-- https://rpubs.com/ials2un/rf_landcover -->
<!-- https://blogs.fu-berlin.de/reseda/classification-in-r/ -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages

```{r libraries, include=FALSE}
# Packages for spatial data processing & visualization
library(rgdal)
library(gdalUtils)
library(raster)
library(sf)
library(sp)
library(terra)
library(RStoolbox)
#library(getSpatialData)
library(rasterVis)
library(mapview)
library(grid)

library(RColorBrewer)
library(plotly)
library(grDevices)

# Machine learning packages
library(caret)
library(randomForest)
library(ranger)
library(MLmetrics)
library(nnet)
library(NeuralNetTools)
library(LiblineaR)

# Packages for general data processing and parallel computation
library(data.table)
library(dplyr)
library(stringr)
library(doParallel)
library(snow)
library(parallel)
library(cvms)

# set the temporary folder for raster package operations
rasterOptions(tmpdir = "./cache/temp")
```

# Data preparation

## Raster data

Import multiband raster

```{r}
# Import raster layer
ls <- raster::stack("D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/L8_reducers_2021_months_8-12.tif")
ls_year <- raster::stack("D:/Dateien/Uni/Eagle_Master/Masterthesis/Data/Landsat/L8_reducer_2021_months_1-12_nuichua/L8_reducers_2021_months_1-12_nuichua.tif")

x <- ls$B_median@file@name
x2 <- ls_year$B_stdDev@file@name

(x <- str_sub(x,-32,-5))   # 8-12 
(x2 <- str_sub(x2,-40,-13))  # 1-12
```

Select bands (predictors)

```{r}
# Subset seasonal median ls image to specific columns
bands <- c("B_median","G_median","R_median","NIR_median","SWIR1_median","SWIR2_median","BSI_median","NDVI_median","EVI2_median", "NDMI_median", "NBR_median","NDWI_median")
landsat <- subset(ls, bands)

# Subset yearly stdDev
stddev <- c("B_stdDev","G_stdDev","R_stdDev","NIR_stdDev","SWIR1_stdDev","SWIR2_stdDev","BSI_stdDev","NDVI_stdDev","EVI2_stdDev", "NDMI_stdDev", "NBR_stdDev","NDWI_stdDev")
year_stddev <- subset(ls_year, stddev)

landsat <- raster::stack(landsat,year_stddev)
names(landsat)
```

Plot median image

```{r, message=FALSE, warning=FALSE}
r <- landsat[[c(1,2,3,4,5)]]
viewRGB(r, r=5, g=4, b=2, layer.name="falsecolor SWIR1-NIR-G")
```

```{r, message=FALSE, warning=FALSE}
viewRGB(r, r=3, g=2, b=1, layer.name="truecolor R-G-B")
```

Plot valid pixels of seasonal scene

```{r, message=FALSE, warning=FALSE}
v <- ls[["valid_pixels"]]
v@data@values <- getValues(v)
levels(v)=data.frame(ID=seq(min(v@data@values),max(v@data@values)), val=seq(min(v@data@values),max(v@data@values)))
mapview(v, layer.name="valid pixels")
```

## Training data

Import training polygons

```{r, message=FALSE, warning=FALSE}
# Import boundary of aoi
aoi <- shapefile("D:/Dateien/Uni/Eagle_Master/Masterthesis/Data/Nui_Chua_NP.shp")

# Import polygons
#samp <- shapefile("D:/Dateien/Uni/Eagle_Master/Masterthesis/Data/trainingdata/Nuichua/LC_classes_tejas.shp")
samp <- shapefile("D:/Dateien/Uni/Eagle_Master/Masterthesis/Data/trainingdata/Nuichua/new-editLP/LC_classes_tejas_new-editLP.shp")

# Need to have a numeric id for each class - helps with rasterization later on.
samp@data$class_id <- as.integer(factor(samp@data$class_id))
samp@data$plot_id <- as.integer(factor(samp@data$plot_id))
#samp@data$binary_id <- as.integer(factor(samp@data$binary_id))

# Set as data table
setDT(samp@data)
```

Define class parameters

```{r}
# set class names
classes <- c("Evergreen.Forest","Dry.Forest","Costal.Shrubland","Inland.Shrubland",
  "Bare.Ground","Agriculture","Water","Built.up")
# define color palette
cpal <- c("#162700","#a1a733","#5fa00a","#37590a","#f86b05","#c22341","#0500ff","#020103")
cpal_az <- c("#c22341","#f86b05","#020103","#5fa00a","#a1a733","#162700","#37590a","#0500ff")

# save class definitions in df
classdf <- data.frame(classvalue = c(1,2,3,4,5,6,7,8),
                      classnames = classes,
                      color = cpal,
                      color_az = cpal_az)
```

<!-- ### Split dataset into training and validation -->

Rasterize training polygons

```{r}
# Create raster template
template_rst <- raster(extent(landsat$B_median), # band B2 has resolution 10 m
                       resolution = 30,
                       crs = projection(landsat$B_median))
#samp_rst <- raster::rasterize(samp, template_rst, field = "class_id") #-> not working, don't know why :(

#samp_rst <- raster("D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/LC_tejas_rasterized_landsat_res.tif") # import sample raster created in QGIS
samp_rst <- raster("D:/Dateien/Uni/Eagle_Master/Masterthesis/Data/trainingdata/Nuichua/new-editLP/trainingsdata_new-editLP_rasterized1.tif")

#mapview(samp_rst)
```

Create random stratified sample points from training polygons

*Sample Methods:*

* *random: Validation samples were picked completely random. Each pixel within the study area has the same probability of being picked.*

* *stratified random: The proportions of the classes in the validation samples correspond to the area proportion on the classification map.That is, the larger the area of class on the map, the more samples will be drawn from it.*

* *equalized stratified random: Ensures, that each class’s sample size is exactly the same regardless of area of class on the map*

```{r}
points <- sampleStratified(samp_rst, size = 1000, xy=TRUE, na.rm = TRUE, sp = TRUE)
points <- points[,-1]
colnames(points@data)[3] = "class_id"
```

Split random stratified samples into training and validation

```{r}
# # Add ID
# points@data$ID <- seq.int(nrow(points@data))

split <- 0.7

# Convert points to data table
poi <- data.frame(points)
poi <- poi[1:3]
poi <- setDT(poi)

# A stratified random split of the data
set.seed(321)
idx_train <- createDataPartition(poi$class_id,
                                 p = split, # percentage of data as training
                                 list = FALSE)
train <- poi[idx_train]
test <- poi[-idx_train]

# Convert to sp objects
train_sp <- SpatialPointsDataFrame(coords = train[, .(x, y)],
                                 data = train %>% select(-c("x","y")) ,
                                 proj4string = samp_rst@crs)
test_sp <- SpatialPointsDataFrame(coords = test[, .(x, y)],
                                 data = test %>% select(-c("x","y")) ,
                                 proj4string = samp_rst@crs)

# Convert class id to factor and set levels to avoid error in training part
train_sp@data$class_id <- as.factor(train_sp@data$class_id)
levels(train_sp@data$class_id) <- as.character(classdf$classnames)

test_sp@data$class_id <- as.factor(test_sp@data$class_id)
levels(test_sp@data$class_id) <- as.character(classdf$classnames)
```

Training samples split into 70% for training and 30% for validation

```{r}
table(train_sp@data$class_id)
table(test_sp@data$class_id)
```

*--> Raster and vector data have same CRS? If not, reproject training data.*

Plot training data. 

In the layer panel (left side) you can select/unselect the different layers and choose other background themes.

```{r}
t1 <- mapview(samp, zcol = "landcover", layer.name = "Tejas landcover classes",
        col.regions = list("#c22341","#f86b05","#020103","#5fa00a","#a1a733","#162700","#37590a","#0500ff"),
        alpha.regions=0.9)
m1 <- mapview(points)
m_train <- mapview(train_sp, col.regions="magenta", color="magenta",layer.name="Training samples",cex=0.5)
m_test <- mapview(test_sp, col.regions="cyan",color="cyan",layer.name="Validation samples",cex=0.5)

t1 +
  #m1 +
  m_train +
  m_test 
```

<!-- ### Alternativ: import already split train and test polygons -->

<!-- worse accuracy than first approach!! -->

<!-- ```{r} -->
<!-- # import training partition (70%) -->
<!-- train_sp <- shapefile("D:/Dateien/Uni/Eagle_Master/Masterthesis/Data/trainingdata/Nuichua/LC_tejas_split/LC_classes_tejas_70percent_training.shp") -->

<!-- # convert class id to factor and set levels to avoid error -->
<!-- train_sp@data$class_id <- as.factor(train_sp@data$class_id) -->
<!-- levels(train_sp@data$class_id) <- as.character(classdf$classnames) -->

<!-- # import validation partition (30%) -->
<!-- test_sp <- shapefile("D:/Dateien/Uni/Eagle_Master/Masterthesis/Data/trainingdata/Nuichua/LC_tejas_split/LC_classes_tejas_30percent_validation.shp") -->

<!-- # convert class id to factor and set levels to avoid error -->
<!-- test_sp@data$class_id <- as.factor(test_sp@data$class_id) -->
<!-- levels(test_sp@data$class_id) <- as.character(classdf$classnames) -->
<!-- ``` -->

<!-- *-> Raster and vector data have same CRS? If not, reproject training data.* -->

<!-- Plot training data.  -->

<!-- In the layer panel (left side) you can select/unselect the different layers and choose other background themes. -->

<!-- ```{r} -->
<!-- t1 <- mapview(samp, zcol = "landcover", layer.name = "Tejas landcover classes", -->
<!--         col.regions = list("#c22341","#f86b05","#020103","#5fa00a","#a1a733","#162700","#37590a","#0500ff"), -->
<!--         alpha.regions=0.9) -->

<!-- t2 <- mapview(train_sp, layer.name = "70% training", -->
<!--         color = "magenta", col.regions="magenta",alpha.regions=0, lwd=1)  -->

<!-- t3 <- mapview(test_sp, layer.name = "30% validation", -->
<!--         color = "cyan", col.regions="cyan",alpha.regions=0, lwd=1) -->

<!-- t1 + t2 + t3 -->
<!-- ``` -->

# RF classification

Set parameters and run superClass() from RStoolbox

```{r }
# SC_prob_l8 <- superClass(landsat,
#                   train_sp,
#                   valData = test_sp,
#                   responseCol = "class_id",
#                   #nSamples = 1000,           # ignored if input is of class spatial points
#                   #polygonBasedCV = TRUE,     # ignored if input is of class spatial points
#                   #trainPartition = 0.7,      # ignored if input valData is provided
#                   model = "rf",
#                   tuneLength = 3,
#                   kfold = 5,
#                   minDist = 1,
#                   mode = "classification",   # regression
#                   predict = TRUE,
#                   predType = "prob",         # raw
#                   #filename = paste0("D:/Dateien/Dropbox (ScreenForBio)/Projects/SBC/SBC_analysis_Nui_Chua/Initial_LC_Luisa/Nuichua/SC_prob_l8_",x,".tif"),
#                   verbose = TRUE)
#                   #overwrite = TRUE)

# # save superclass object
# save(SC_prob_l8, file = paste0(
#   #"D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/SC/SC_prob_",x,"_year_stddev.RData"
#   "D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/processed/Classification/R/Landsat/30cloudprob_11.4/SC_prob_",x,"_year_stddev.RData"
# ))



#load superclass object
load(
#"D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/SC/SC_prob_L8_reducers_2021_months_8-12_year_stddev.RData"
"D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/processed/Classification/R/Landsat/30cloudprob_11.4/SC_prob_L8_reducers_2021_months_8-12_year_stddev.RData"
)
```

## Multiband probability layer

```{r}
prob_stack <- SC_prob_l8$map
rasterVis::levelplot(prob_stack)
```

```{r, warning=FALSE, message=FALSE}
# for (i in 1:length(classdf$classvalue)){
#   mycol <- colorRampPalette(c("white", classdf$color[i]))
#   print(mapview(prob_stack[[i]], col.regions=mycol, layer.name=classdf$classnames[i]))
# }

mycol1 <- colorRampPalette(c("white", classdf$color[1]))
mycol2 <- colorRampPalette(c("white", classdf$color[2]))
mycol3 <- colorRampPalette(c("white", classdf$color[3]))
mycol4 <- colorRampPalette(c("white", classdf$color[4]))
mycol5 <- colorRampPalette(c("white", classdf$color[5]))
mycol6 <- colorRampPalette(c("white", classdf$color[6]))
mycol7 <- colorRampPalette(c("white", classdf$color[7]))
mycol8 <- colorRampPalette(c("white", classdf$color[8]))

mapview(prob_stack[[1]], col.regions=mycol1, layer.name=classdf$classnames[1])
mapview(prob_stack[[2]], col.regions=mycol2, layer.name=classdf$classnames[2])
mapview(prob_stack[[3]], col.regions=mycol3, layer.name=classdf$classnames[3])
mapview(prob_stack[[4]], col.regions=mycol4, layer.name=classdf$classnames[4])
mapview(prob_stack[[5]], col.regions=mycol5, layer.name=classdf$classnames[5])
mapview(prob_stack[[6]], col.regions=mycol6, layer.name=classdf$classnames[6])
mapview(prob_stack[[7]], col.regions=mycol7, layer.name=classdf$classnames[7])
mapview(prob_stack[[8]], col.regions=mycol8, layer.name=classdf$classnames[8])
```

## Singleband classification layer

```{r, warning=FALSE,message=FALSE}
# Combine probability layers to one final layer product by selecting the max probability value
which.max2 <- function(x, ...) which.max(x)           # helper function to absorb "na.rm"
raw <-  stackApply(prob_stack, rep(1,8), fun=which.max2, na.rm=NULL)
levels(raw)=data.frame(ID=1:8, class=classdf$classnames)

mapview(raw, col.regions=list("#162700","#a1a733","#5fa00a","#37590a","#f86b05","#c22341","#0500ff","#020103"), alpha.regions=1, layer.name="L8 LC classification")
```



## Model evaluation

### Accuracy assessment 

Confusion matrix, overall accuracy, kappa, class statistics

```{r}
# validation performance estimates based on independent validation (confusion matrix etc.)
SC_prob_l8$validation$performance
```

### Predictor importance

```{r}
caret::varImp(SC_prob_l8$model)$importance %>% 
  as.matrix %>% 
  plot_ly(x = colnames(.), y = rownames(.), z = ., type = "heatmap",
          width = 600, height = 600)
```

### Modelstatistics

```{r}
# the fitted model
SC_prob_l8$model

# model fit statistics
SC_prob_l8$modelFit

# # indexes of samples used for training
# SC_prob_l8$training
# 
# # actual pixel coordinates plus reference and predicted values used for validation
# SC_prob_l8$validation$validationSamples
# 
# # validation polygpns (clipped with mindist to training geometries)
# SC_prob_l8$validation$validationGeometry
# 
# # the predicted raster
# SC_prob_l8$map
# 
# # data.frame containing an integer <-> label mapping
# SC_prob_l8$classMapping
```

### Export

```{r}
exp1 <- terra::rast(prob_stack)
writeRaster(exp1,paste0(
  #"D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/SC/SC_prob_",x,"_year_stddev.tif"
  #"D:/Dateien/Dropbox (ScreenForBio)/Projects/SBC/SBC_analysis_Nui_Chua/Initial_LC_Luisa/Nuichua/SC_prob_",x,"_year_stddev.tif"
  "D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/processed/Classification/R/Landsat/30cloudprob_11.4/SC_prob_",x,"_year_stddev.tif"
))

exp2 <- terra::rast(raw)
writeRaster(exp2,paste0(
  #"D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/SC/SC_raw_",x,"_year_stddev.tif"
  #"D:/Dateien/Dropbox (ScreenForBio)/Projects/SBC/SBC_analysis_Nui_Chua/Initial_LC_Luisa/Nuichua/SC_raw_",x,"_year_stddev.tif"
    "D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/processed/Classification/R/Landsat/30cloudprob_11.4/SC_raw_",x,"_year_stddev.tif"
))
```

## Visualize extraced band values

Create spatial points from all cells in training polygons

```{r}
samp_dt <- as.data.table(rasterToPoints(samp_rst))
setnames(samp_dt, old = "trainingsdata_new.editLP_rasterized1",
                        #"LC_tejas_rasterized", 
                  new = "class_id")

samp_points <- SpatialPointsDataFrame(coords = samp_dt[, .(x, y)],
                                 data = samp_dt,
                                 proj4string = samp_rst@crs)

mapview(samp_points,zcol="class_id",layer.name="Point class ids",
        col.regions = list("#162700","#a1a733","#5fa00a","#37590a","#f86b05","#c22341","#0500ff","#020103"))
```

Extract bandinfos from landsat image at points

<!-- # alternativ: data.table syntax -->
<!-- dt <- terra::rast(landsat) %>% -->
<!--   terra::extract(y = vect(points)) %>% -->
<!--   as.data.table %>% -->
<!--   .[, class_id := points@data$class_id] # %>%  # add the class names to each row -->
<!--   # merge(y = unique(samp@data), by.x = "class_id", by.y = "ID", all = TRUE, sort = FALSE) %>% -->
<!--   # .[, class_id := NULL] %>% # this column is extra now, delete it -->
<!--   # .[, class := factor(class)] -->

```{r}
# dplyr syntax
dt1 <- terra::rast(landsat) %>%
  terra::extract(y = terra::vect(samp_points)) %>%
  as.data.frame %>%
  mutate(class_id = samp_points@data$class_id) %>% # add the class names to each row
  mutate(lat = samp_points@data$x) %>% # add the class names to each row
  mutate(long = samp_points@data$y) %>%
  # left_join(y = unique(poly@data), by = c("class_id" = "id")) %>%
  # mutate(class_id = NULL) %>% # this column is extra now, delete it
  mutate(class_id = factor(class_id))

data.table::setDT(dt1)

# Add landcover labels
dt <- dt1 %>%
  mutate(landcover = case_when(
    class_id == 1 ~ "Evergreen",
    class_id == 2 ~ "Dry Forest",
    class_id == 3 ~ "Coastal Shrubland",
    class_id == 4 ~ "Inland Shrubland",
    class_id == 5 ~ "Bare Ground",
    class_id == 6 ~ "Agriculture",
    class_id == 7 ~ "Water",
    class_id == 8 ~ "Built-up")) %>%
  mutate(landcover = factor(landcover))

# View the first 6 rows
#head(dt)
```

### Bandvalues per class

Samples per class

```{r, warning=FALSE,message=FALSE}
df <- data.frame(dt)
df_prep <- df %>% select(-c("ID","class_id","lat","long"))
df2 <- reshape2::melt(df_prep)
sample_size <- df2 %>% group_by(landcover) %>% summarize(num=n())
sample_table <- cbind(data.frame(c(6,5,8,3,2,1,4,7)), sample_size)
colnames(sample_table) <- c("Class ID", "Landcover", "Number of samples")
DT::datatable(sample_table,
              options = list(dom = 't'),
              #class = 'cell-border stripe',
              rownames=FALSE)
```

Plot value distribution

<!-- facet_wrap ncol=3: {r, warning=FALSE, message=FALSE, fig.height=45, fig.width=20, out.width="100%"} -->

```{r, warning=FALSE, message=FALSE, fig.height=65, fig.width=15, out.width="100%"}
plot <- df2 %>%
  #left_join(sample_size) %>%
  #mutate(myaxis = paste0(landcover, "\n", "n=", num))  %>%
  ggplot(aes(x = landcover, y = value, fill=landcover)) +
  geom_violin(trim = FALSE,                            # avoid trimming the trails
              draw_quantiles = c(0.25, 0.5, 0.75)) +     # add quantiles
  #geom_boxplot(width = 0.07,position = position_dodge(width = 0.9)) +
  scale_fill_manual(values = cpal_az) +
  theme(text = element_text(size = 20)) +
  theme(axis.text.x = element_text(angle = 45)) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none") +
  ggtitle("Value distribution of band samples per landcover class \n") +
  facet_wrap(facets = vars(variable), ncol = 2, scales = "free")     #~variable, 
plot
```

<!-- ```{r} -->
<!-- #save(plot, file="D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/facet_wrap_plot.RData") -->
<!-- #save(sample_table, file="D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/sample_table.RData") -->
<!-- ``` -->

### Spectral profiles per class

*They represent the mean values of each class for the individual spectral bands.*

<!-- *You can also represent other features, e.g., terrain height or precipitation, however, you must then pay attention to the value range in the presentation and possibly normalize the data at first. The magic here happens in the aggregate() command, which combines all the rows of the same class . ~ landcover and calculates the arithmetic mean of those groups FUN = mean.* -->

Color channels: median over season, standard deviation over year

```{r}
# Normalize other than spectral bands
#...

# Aggregate dataset
sp <- aggregate( . ~ landcover, data = dt, FUN = mean, na.rm = TRUE )

# Split predictors and select only spectral bands
median <- sp %>% select(landcover | ends_with("median")) %>% cbind(sp$landcover) %>% select(c(1:7))
stdDev <- sp %>% select(landcover | ends_with("stdDev")) %>% select(c(1:7))

l <- list(median, stdDev)

for (k in 1:length(l)){
  
  # plot empty plot of a defined size
  plot(0,
       ylim = c(min(l[[k]][2:ncol(l[[k]])]), max(l[[k]][2:ncol(l[[k]])])), 
       xlim = c(1, ncol(l[[k]])-1), 
       type = 'n', 
       xlab = "L8 bands", 
       ylab = "reflectance [% * 100]",
       xaxt = "n"
       )
  axis(1, at=1:(length(median)-1), labels=c(colnames(l[[k]]))[-1], cex.axis=0.8)

    # draw one line for each class
    for (i in 1:nrow(l[[k]])){
      lines(as.numeric(l[[k]][i,-1]), 
            lwd = 4, 
            col = classdf$color_az[i]
            )
      }

  # add a grid
  grid()
  
  # add a legend
  legend(as.character(sp$landcover),
         x = "topleft",
         col = classdf$color_az,
         lwd = 4,
         bty = "n"
         )

}
rm(median, stdDev, l)
```

Indices: median over season, standard deviation over year

```{r}
# Split predictors and select only indices
median <- sp %>% select(landcover | ends_with("median")) %>% select(-c(1:7))
stdDev <- sp %>% select(landcover | ends_with("stdDev")) %>% select(-c(1:7))

l <- list(median, stdDev)

for (k in 1:length(l)){
  
  # plot empty plot of a defined size
  plot(0,
       ylim = c(min(l[[k]][2:ncol(l[[k]])]), max(l[[k]][2:ncol(l[[k]])])), 
       xlim = c(1, ncol(l[[k]])-1), 
       type = 'n', 
       xlab = "L8 bands", 
       ylab = "reflectance [% * 100]",
       xaxt = "n"
       )
  axis(1, at=1:(length(median)-1), labels=c(colnames(l[[k]]))[-1], cex.axis=0.8)

    # draw one line for each class
    for (i in 1:nrow(l[[k]])){
      lines(as.numeric(l[[k]][i,-1]), 
            lwd = 4, 
            col = classdf$color_az[i]
            )
      }

  # add a grid
  grid()
  
  # add a legend
  legend(as.character(sp$landcover),
         x = "topleft",
         col = classdf$color_az,
         lwd = 4,
         bty = "n"
         )

}
rm(median, stdDev, l)
```

### Histograms of predictors

```{r}
dt %>%
  select(-c("class_id","landcover","lat","long","ID")) %>%
  select(ends_with("median")) %>%
  melt(measure.vars = names(.)) %>%
  ggplot() +
  geom_histogram(aes(value)) +
  geom_vline(xintercept = 0, color = "gray70") +
  facet_wrap(facets = vars(variable), ncol = 4)
```

```{r}
dt %>%
  select(-c("class_id","landcover","lat","long","ID")) %>%
  select(ends_with("stdDev")) %>%
  melt(measure.vars = names(.)) %>%
  ggplot() +
  geom_histogram(aes(value)) +
  geom_vline(xintercept = 0, color = "gray70") +
  facet_wrap(facets = vars(variable), ncol = 4)
```


<!-- ```{r} --
<!-- #save.image(file="D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/SC/superclass_RF_landsat8_workspace.RData") -->

<!-- #load("D:/Dateien/Uni/Eagle_Master/Masterthesis/R_Masterthesis_SBC/testing/SC/superclass_RF_landsat8_workspace.RData") -->
<!-- ``` -->


